Supplementary Material for ``Evaluating infectious disease forecasts with allocation scoring rules''

### 2023-12-08 alloscore_manuscript/supplement.rnw
bayes risk error idea

Exact computation of the allocation score $S_A(F, y; K)$ of a forecast $F$ requires an explicit choice of and expression for a 
solution $\bm{q}_{\tau^{\star},F} \in \undertilde{\bm{F}}^{-1}(\tau^{\star})$ to \eqref{eqn:quantiles-sum-to-K} where
$\tau^{\star}$ solves \eqref{eqn:tau-inclusion}. For practical scenarios in which the forecast $F$ has a form preventing 
analytical solutions to \eqref{eqn:quantiles-sum-to-K}, we must develop a method to approximate solutions to \eqref{eqn:tau-inclusion}
which lead to adequate approximations of the linear program
\begin{align}
\sum_{x \in \undertilde{\bm{F}}^{-1}(\tau^{\star})}x_i = K.
\end{align}

>>>>

Exact computation of the allocation score $S_A(F, y; K)$ of a forecast $F$ requires an explicit choice of and expression for a 
solution $x^{F,K} = \bm{q}_{\tau^{\star},F} \in \undertilde{\bm{F}}^{-1}(\tau^{\star})$ to \eqref{eqn:quantiles-sum-to-K} where
$\tau^{\star}$ solves \eqref{eqn:tau-inclusion}. For practical scenarios in which the forecast $F$ has a form preventing 
analytical solutions to \eqref{eqn:quantiles-sum-to-K}, we seek a method of generating an approximation $\tilde{\tau}$ to 
a solution $\tau^{\star}$ which offers control (at least in principle) of the Bayes risk error
\begin{align}
\left|\mathbb{E}_F[s_A(\bm{q}_{\tilde{\tau},F}, Y)] - \mathbb{E}_F[s_A(x^{F,K}, Y)]\right|
\end{align}
where $\bm{q}_{\tilde{\tau},F}$ solves the linear program
$\sum_{x \in \undertilde{\bm{F}}^{-1}(\tilde{\tau})}x_i = K$.
